There once was a grid at ol' Carkeek

### 2016-04-14 Manuscript/v0.0/carkeek_grid.tex
small changes to dissimilarity

% We measure 'extra-(corporeal|organismal) DNA
Some authors have cautioned against the use of DNA-based macrobial communities in marine environments because they are subject to dynamic physical forces (CITE).
If environmental circulation 
In general, the relationship between community dissimilarity (0 = identical; 1 = completely different) and spatial distance is expected to be asymptotic, because communities nearer to each other tend to be more similar than those farther apart.
The intercept is expected to be near 0, because samples taken at the same place should be very similar. % technically impossible for samples to be taken at exactly 0; they are actually immediately adjacent.
Deviation in the intercept from 0 indicates heterogeneous community composition/structure over fine scales.
A flat relationship between dissimilarity and distance indicates that heterogeneity is not assorted spatially, and can be interpreted in different ways, depending on the mean.
If the mean is near 1, the spatial heterogeneity has overwhelmed the spatial scale of sampling.
If the mean is near 0, there is no community heterogeneity over the scale sampled.

>>>>

% We measure 'extra-(corporeal|organismal) DNA
Some authors have cautioned against the use of DNA-based macrobial communities in marine environments because they are subject to dynamic physical forces (CITE).
%If environmental circulation 
In general, the relationship between community dissimilarity (0 = identical; 1 = completely different) and spatial distance is expected to be asymptotic, because communities nearer to each other tend to be more similar than those farther apart.
The intercept is expected to be 0, because only within-sample comparisons can have 0 spatial separation, and communities have no dissimilarity within a sample. % technically impossible for samples to be taken at exactly 0; they are actually immediately adjacent.
Deviation in the intercept from 0 indicates heterogeneous community composition/structure over fine scales.
A flat relationship between dissimilarity and distance indicates that heterogeneity is not assorted spatially, and can be interpreted in different ways, depending on the mean.
If the mean is 1, the spatial heterogeneity has overwhelmed the spatial scale of sampling.
If the mean is 0, all samples are identical, and we infer there is complete community homogeneity over the scale sampled.
